---
title: "NathanielPart2"
output: html_document
date: "2023-01-31"
---

ACS = American Community Survey

#### Radon Data

a.  The data was created by the Minnesota Department of Health

b.  Each observation is a Census Tract, a subdivision of a county. The data measures the rate of radon testing and the results of those tests.

c.  The data set only has information on radon testing, there is no accompanying demographic information. The radon concentration value is only an estimate and may be far off in tracts with few tests.

d.  The data has variables for the average yearly properties radon tested, the median radon value, and the percent of properties testing above a certain threshold by county.

e.  

```{r packages}
library(tidyverse)
library(readr)
library(ggplot2)
```

```{r load data}
radon<-read.csv("RadonTract.csv") #https://mndatamaps.web.health.state.mn.us/interactive/radontract.html
acs<-read.csv("CensusACSTract.csv") #https://gisdata.mn.gov/dataset/us-mn-state-metc-society-census-acs
```

```{r clean data}
radonTract <- radon %>% filter(!(county == "MINNESOTA"))
```

```{r,warning=FALSE,message=FALSE}
radonTract %>% ggplot() +
  geom_point(aes(x=TotalHousingUnits,y=AverageAnnualNumber))+
  labs(x="Total Housing Units",y="Average Annual Radon Tests", title = "Housing Units and Radon Tests by Census Tract") +
  theme_light()
```

#### Census Data

a.  This data is from the US Census Bureau via the Minnesota Government.

b.  Each observation is a census tract, same as first data set.

c.  The data is not from the actual census but the American Community Survey. That is, the data is just an estimate based on surveys.

d.  <https://resources.gisdata.mn.gov/pub/gdrs/data/pub/us_mn_state_metc/society_census_acs/metadata/metadata.html>

    has a list of the variables included and their definitions. Those of most interest to us are about housing, poverty rates, and measures of health and disability.

e.  

```{r,warning=FALSE,message=FALSE}
acs %>% ggplot() + 
  geom_point(aes(x=HUSFD/HUTOTAL,y=POV100RATE))+
  geom_smooth(aes(x=HUSFD/HUTOTAL,y=POV100RATE), se = FALSE, color="darkred")+
  labs(x="Percent Single Family Detached Housing",y="Poverty Rate at 100% Poverty Level",title="Detached Housing and Poverty by Census Tract")+
  theme_light()
```

4. 

Join by Census Tract, of course.